Output Summary

### 2020-10-20 03-post-process/output-plots.Rmd
Add new parameters to output plots

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
)

@@

```{r abundance-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
plot_tseries(post_summ(post, "^Mb[.+,2]$"), jags_data$Mb_obs[observable,2], main = "Spring Trap Abundance")
plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Abundance")
```

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)

>>>>

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
  "^phi_Mb_M["
)

@@

```{r abundance-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = "Spring Trap Abundance")
plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Abundance")
```

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_M`: mean probability of surviving from hatchery release in spring to estuary (hatchery fish)
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)
